The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-20 project/paper/intro.tex
Added footnotes (defn's, thm statements)

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with pdf

@@

where $q=1-p$. Calculating the binomial cdf, $F_X(x) = P(X \leq x) =
\sum_{k=1}^x f_X(k)$, by hand is manageable for small $n$ but quickly becomes
cumbersome as $n$ grows even moderately large. A common strategy is to use the
normal distribution as an approximation:

@@

where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.

>>>>

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with probability density function (pdf)

@@

where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
strategy is to use the normal distribution as an approximation:

@@

where $\Phi$ is the standard normal\footnote{Let $X \sim Z = N(0, 1)$. Then $X$
is said to be a standard normal distribution with pdf

\begin{equation*}
  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
\end{equation*}

and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t) \; dt$. Equations 3.3.29
and 3.3.30, \citet{textbook}.} cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.

### 2011-01-20 project/paper/output.tex
Added footnotes (defn's, thm statements)

  We will now show that $\phi^2 \sim \chi^2_1$:

@@

  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
  can then transform each piece separately using Theorem 6.3.2 from
  \citet{textbook}:

@@

  Then, by Theorem 6.3.10 from \citet{textbook},

>>>>

  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
  generating function (mgf):\footnote{If $X$ is a random variable, then the
  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
  (mgf) of X if this expected value exists for all values of $t$ in some
  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
  \citet{textbook}.}

@@

  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
  can then transform each piece separately using Theorem 6.3.2 from
  \citet{textbook}:\footnote{\textbf{Continuous transformations that are
  one-to-one} (Theorem 6.3.2, \citealp{textbook}): Suppose that $X$ is a
  continuous random variable with pdf $f_X(x)$, and assume that $Y = u(X)$
  defines a one-to-one transformation from $A = \{x|f_X(x) > 0\}$ on to $B =
  \{y|f_Y(y) > 0\}$ with inverse transformation $x = w(y)$. If the derivative
  $(d/dy)w(y)$ is continuous and nonzero on $B$, then the pdf of $Y$ is

  \begin{equation}
    \label{eq:transformations-1-to-1}
    f_Y(y) = f_X(w(y)) \left| \frac{d}{dy} w(y) \right| \qquad y \in B.
  \end{equation}

  \label{fnote:transformations-1-to-1}
  }

@@

  Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
  transformations that are not one-to-one} (Equation 6.3.10,
  \citealp{textbook}): When $u(x)$ is not one-to-one over $A$, we can replace
  equation \eqref{eq:transformations-1-to-1} in footnote
  \ref{fnote:transformations-1-to-1} with

  \begin{equation*}
    f_Y(y) = \sum_j f_X(w_j(y)) \left| \frac{d}{dy} w_j(y) \right|.
  \end{equation*}
  }

### 2011-01-20 project/paper/properties.tex
Finished demonstration of calculating sn by hand
Added footnotes (defn's, thm statements)

  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
  \Phi(\lambda z)$ conforms to equation
  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
  and $Z$ are equal in distribution.

  We will now show that $\phi^2 \sim \chi^2_1$:

>>>>

  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
  \Phi(\lambda z)$ conforms to Equation
  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
  and $Z$ are equal in distribution.

  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
  generating function (mgf):\footnote{If $X$ is a random variable, then the
  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
  (mgf) of X if this expected value exists for all values of $t$ in some
  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
  \citet{textbook}.}
